---
title: 'Reproducible Research: Peer Assessment 1'
output:
  html_document:
    keep_md: yes
  pdf_document: default
  word_document: default
---


## Loading and preprocessing the data
```{r}
originData<-read.csv("activity.csv")
summary(originData)

```



## What is mean total number of steps taken per day?

For this part of the assignment, you can ignore the missing values in the dataset.

1. Make a histogram of the total number of steps taken per day   

```{r}
# Remove row with NA in the dataset
data<-originData[complete.cases(originData),]
summary(data)
#change date character to date format
data$date<-as.Date(data$date,"%Y-%m-%d")

#Make histogram
library(ggplot2)
library(scales)
g<-ggplot(data,aes(date,steps))
g+geom_histogram(stat="identity")+
        scale_x_date( labels=date_format("%b%e"),breaks = date_breaks("week"))+
        labs(x="",y="Total steps per day")
```

2. Calculate and report the mean and median total number of steps taken per day


```{r}
library(plyr)
StepPerDay<-ddply(data,c("date"),summarise,steps=sum(steps))
summary(StepPerDay)
```
The mean total number of step per day was 10766 (steps)
the median was 10765 steps.

## What is the average daily activity pattern?

```{r}

StepPerInt<-ddply(data,c("interval"),summarise,steps=mean(steps))

plot(StepPerInt$interval,StepPerInt$steps)
```

The interval has maximum average of number of steps
```{r}
StepPerInt[StepPerInt$steps==max(StepPerInt$steps),]
```

835 is the interval time that the average of number of steps is maximum (~206 steps)

## Imputing missing values
1. I will impute the NA by average value of that interval

```{r}
ImpData<-originData # create a new imputed data frame
i<-1

while (i<=nrow(ImpData)){
        if (is.na(ImpData$steps[i])){
                j<-ImpData$interval[i]
                ImpData[i,1]<-StepPerInt[StepPerInt$interval==j,]$steps
        }
        i<-i+1
}
#View summary of imputed data
summary(ImpData)
```
There was no NA now.

2. Make histogram of mean daily steps

```{r}
#change format of character into date
ImpData$date<-as.Date(ImpData$date,format="%Y-%m-%d")

#Make histogram by using ggplot2 and scales packages
library(ggplot2)
library(scales)
his<-ggplot(ImpData,aes(date,steps))
his+geom_histogram(stat="identity")+
        scale_x_date( labels=date_format("%b%e"),breaks = date_breaks("week"))+
        labs(x="",y="Total steps per day")
```

3. Calculate the mean and median of total steps per day
```{r}
# Make table data
StepPerDay1<-ddply(ImpData,c("date"),summarise,steps=sum(steps))

#Caculate mean and median
summary(StepPerDay1)
```

We can now see that mean of total steps per day was not changed. However, median
of total steps per day in imputed data has changed toward the mean value.

## Are there differences in activity patterns between weekdays and weekends?

1.Format the day to become weedays and weekends

```{r}
#Change date format into day
ImpData$date<-format(ImpData$date,"%a",trim=T)
table(ImpData$date) #View number of date now

#Change date to weekday and weekend
for (i in 1:nrow(ImpData)){
        ifelse(ImpData$date[i]=="Sat" | ImpData$date[i]=="Sun",
                ImpData[i,2]<-"Weekend",
               ImpData[i,2]<-"Weekday" )}

str(ImpData)
```

2. Make graph to see steps by interval in weekday and weekend

```{r}
library(ggplot2)
we<-ggplot(ImpData,aes(interval,steps))
we+geom_line()+facet_grid(date~.)+
        labs(x="Time",y="Average total of steps")+
        theme(strip.text.y=element_text(size=15,color="red"))+
        theme(axis.title.x=element_text(size=15))+
        theme(axis.title.y=element_text(size=15))
```

We can see that in the weekday, the high activity start earlier from 5 AM, while
for the weekend, the acitivity start late at around 8 AM.
after 8 AM.