---
title: 'Reproducible Research: Peer Assessment 1'
output:
  word_document: default
  html_document:
    keep_md: yes
---


## Loading and preprocessing the data
```{r}
data<-read.csv("activity.csv")
summary(data)

```

## What is mean total number of steps taken per day?

For this part of the assignment, you can ignore the missing values in the dataset.

1. Make a histogram of the total number of steps taken each day   

```{r}
Nadata<-data[complete.cases(data),]# Remove row with NA
summary(Nadata)
library(ggplot2)
g<-ggplot(Nadata,aes(date,steps))
g+geom_histogram(stat="identity")
```

2. Calculate and report the mean and median total number of steps taken per day

```{r}
library(data.table)
TableNadata<-data.table(Nadata)
StepPerDate<-TableNadata[,.(steps=sum(steps)),by=date]
summary(StepPerDate$steps)

```


## What is the average daily activity pattern?

```{r}

StepPerInt<-TableNadata[,.(steps=mean(steps)),by=interval]
plot(StepPerInt$interval,StepPerInt$steps)
```

The interval across the day, which have maximum average of number of step
```{r}
StepPerInt[steps==max(StepPerInt$steps),]

```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
